ISYE 6501

### 2022-12-05 project/submission_project.Rmd
project report v0
hw4

-   [Summary](#Summary)
-   [Backfround on Bharat Pe](#background)
-   [Analytics Usecases](#usecases)
-   [Usecase 1: Lending Activity](#usecase1)
-   [Usecase 2:](#usecase2)
-   [Usecase 3:](#usecase3)

@@

## Backfround on BharatPe and UPI {#background}

### BharatPe

[BharatPe](https://bharatpe.com/companyprofile)

### UPI

[UPI](https://www.npci.org.in/what-we-do/upi/product-overview)

monthly transactions. BharatPe was one of the key players to ride this wave of digital (UPI) payments.

monthly transactions. BharatPe was one of the key players to ride this wave of digital (UPI) payments.

### Analytics Usecases {#usecases}

## Usecase 1: Lending Activity {#usecase1}

@@

### Classification Model: To Lend or not ?

### Regression Model: How much to lend ?

## Usecase 2: Personalisation Services

>>>>

-   [Summary](#Summary)
-   [Backfround on Zepto](#background)
-   [Analytics Usecases](#usecases)
-   [Usecase 1: Lending Activity](#usecase1)
-   [Usecase 2:](#usecase2)
-   [Usecase 3:](#usecase3)

@@

## Backfround on Zepto {#background}

## Problem Definition {#usecases}

## Modelling Methodology {#usecase1}

@@

```{r,echo=FALSE, out.width = "80%", fig.align = "center"}
knitr::include_graphics("./6501_usecase1.drawio.png")
```

###
